---
title: "2020 IR Lake Analysis Preprocessing Data"
author: "Emma Jones"
date: "February 25, 2019"
output: html_document
---

This script continues the process of organizing lake station information for the 2020 IR lakes assessment. It was built in R version 3.5.2 "Eggshell Igloo."

This script picks up where dataPreprocessing_Statewide.Rmd left off. Prior to being able to run the lakes assessment app, we need to do a little data testing. 

Preliminary Step: set up R working environment
```{r setup, include=TRUE, message=FALSE}
library(tidyverse) # Data analysis extraordinaire
library(readxl) # To read in Excel Workbooks
library(sf)
```

1) Start with nearly organized data from dataPreprocessing_Statewide.Rmd, the RegionalResultsLake_RegionCode.csv dataset. These stations were originally from Roger's data pull and the assessor went through the process of attaching AU and WQS information to the sites as well as splitting up the riverine and lacustrine sites. 

1a) The RegionalResultsLake_RegionCode.csv dataset needs to be copied from the Rivers-StreamsAssessment/processedStationData/ directory to the LakesAssessment/processedStationData/ directory in order to utilize that dataset in this project.

```{r bring in RegionalResults}
RegionalResultsLake <- read_csv('app2020/processedStationData/RegionalResultsLake_BRRO.csv')# the exact dataset name will depend on your assessment region
```

# Need lake name to attach StationID's to lake Chla and TP limits
To do this we will bring in data from last available cycle (2016 IR here but needs to be updated to 2018IR when data is available). There are 255 AU's in the 2016 IR, one additional from 2014
# table was exported from VA_ADB_2016_final.mdb, tblAllLakes_2016 table 

2) Bring in ADB tblAllLakes

```{r tblAllLakes}
allLakes <- readxl::read_excel('app2020/data/tblAllLakes_2016.xlsx',sheet='tblAllLakes_2016')
unique(allLakes$WATER_NAME)
unique(allLakes$ID305B)
```

All stations should connect to allLakes dataframe, but if not need to manually fix it because we need the lake name to connect Chl a and TP limits to stations by lake name.
 
```{r join tblAllLakes to RegionalResults}
# make common ID305B column based on the ID3
RegionalResultsLake2 <- mutate(RegionalResultsLake, ID305B = ID305B_1) %>% #ifelse(STATION_TYPE_1 == 'L',ID305B_1, 
                                                            #        ifelse(STATION_TYPE_2 =='L', ID305B_2,
                                                            #               ifelse(STATION_TYPE_3 == 'L', ID305B_3, ID305B_1)))) %>%
  #select(ID305B_1, ID305B_2, ID305B_3, STATION_TYPE_1, STATION_TYPE_2, STATION_TYPE_3, ID305B, everything())
  left_join(allLakes, by = c('ID305B'))

# try to get connection with ID305B_2 designation

RegionalResultsLake3 <- filter(RegionalResultsLake2, is.na(SIGLAKENAME)) %>%
  select(FDT_STA_ID:ID305B) %>%
  mutate(ID305B = ID305B_2) %>%
  left_join(allLakes, by = c('ID305B'))
# didn't improve anything
rm(RegionalResultsLake3)

nrow(filter(RegionalResultsLake2, is.na(SIGLAKENAME)))/nrow(RegionalResultsLake2)
```

So over 1/3 of sites dont connect to allLakes database. Probably due to ID305B issues between 2016 IR and 2018 IR. Will have to fix better when get final dataset but for now all I can do is filter those sites out.

```{r no sig lake}
RegionalResultsLake2 <- filter(RegionalResultsLake2, !is.na(SIG_LAKE))
```

Now that we have significant lake designation, we can attach Chl a and TP limits for each lake.

```{r ChlaTP join}
# Transform 9VAC25-260-187 Individual lake standards for nutrients into a table
# from https://leg1.state.va.us/cgi-bin/legp504.exe?000+reg+9VAC25-260-187
# I copy/pasted the table into excel and saved as .csv
lakeNutStandards <- read_csv('app2020/data/9VAC25-260-187lakeNutrientStandards.csv')%>%
  mutate(SIGLAKENAME=`Man-made Lake or Reservoir Name`) %>%
  mutate(SIGLAKENAME = recode(SIGLAKENAME, `Martinsville Reservoir (Beaver Creek Reservoir)`='Martinsville (Beaver Creek) Reservoir' )) # fix known name issues
colnames(lakeNutStandards)[3:4] <- c('Chlorophyll_A_limit','TPhosphorus_limit')

lakeStations <- left_join(RegionalResultsLake2,lakeNutStandards,by='SIGLAKENAME')

```

Need to find ASSESS_TYPE (lacustrine zone or not).

To make a shapefile of previous LZ sites, bring in 2018IR final lake stations
```{r}
lakeStationsFinal <- readRDS('app2020/data/lakeStationsFinal.RDS') %>%
  st_as_sf(coords = c("DD_LONG", "DD_LAT"),  # make spatial layer using these columns
           remove = F, # don't remove these lat/lon cols from df
           crs = 4326) # add coordinate reference system, needs to be geographic for now bc entering lat/lng,

lakeStationsFinalLZ <- filter(lakeStationsFinal, Assess_TYPE== 'LZ')
st_write(lakeStationsFinal, 'app2020/GIS/lakeStationsFinal2018IR.shp')
st_write(lakeStationsFinalLZ, 'app2020/GIS/lakeStationsFinal2018IR_LZ.shp')
```


When I get a polygon of lacustrine zone, I need to make lakeStations into sf object, st join them( st_join(conventionals_D, assessmentLayerSelection, join = st_intersects) ) and where join succesful then mutate column Assess_Type=LZ.

For now, I will force with last cycle's station information just to keep moving.

```{r use last cycle LZ info}
lakeStations2 <- left_join(lakeStations, select(lakeStationsFinal, FDT_STA_ID, Assess_TYPE), by = 'FDT_STA_ID') %>%
  dplyr::select(FDT_STA_ID:TPhosphorus_limit, Assess_TYPE)
```



Save that for starting point of updating app.

```{r}
saveRDS(lakeStations2, 'app2020/data/lakeStations2020.RDS')
```












2)  2016 WQMS GIS data brought in from X:\2016_Assessment\GIS_2016\MonitoringStations copied to a local location. ** NEEDS TO BE UPDATED TO 2018 IR final version when data becomes available **

```{r last cycle mon stations}
wqms_2016 <- st_read('app2020/GIS/va_16ir_wqm_stations.shp') #not final version
```




# Transform 9VAC25-260-187 Individual lake standards for nutrients into a table
# from https://leg1.state.va.us/cgi-bin/legp504.exe?000+reg+9VAC25-260-187
# I copy/pasted the table into excel and saved as .csv
lakeNutStandards <- read_csv('data/9VAC25-260-187lakeNutrientStandards.csv')%>%
  mutate(SIGLAKENAME=`Man-made Lake or Reservoir Name`)
colnames(lakeNutStandards)[3:4] <- c('Chlorophyll_A_limit','TPhosphorus_limit')

